---
title: "Paper flow"
author: "Gurudev Ilangovan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: tibble
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: false
      smooth_scroll: true
    number_sections: true 
    code_folding: hide
---

```{r setup, results="hide"}
knitr::opts_chunk$set(cache = F, message = FALSE)
source("R/paper2/utils.R")
theme_set(theme_light())
```

# Data Generation - The pipeline

## Preprocessing

1. Read April 2013 data and March 17 data. 
2. Do some basic preprocessing
  - Assign ids
  - Calculate age from birth year
  - Add scaled frequencies
```{r preprocess}

df_dob <- 
  read_csv("data/paper2/raw/dob.csv", 
             col_types = cols(voter_registration_number = "c")) %>% 
  select(voter_reg_num = voter_registration_number, dob = bday)

(df_a <- 
    read_delim("data/paper2/raw/apr13.txt", delim = "\t") %>% 
    rename(name_suffix = name_sufx_cd,
           mname = midl_name) %>% 
    mutate_if(is.character, str_squish) %>% 
    mutate(id_a = row_number()))

  
(df_b <- 
    read_delim("data/paper2/raw/mar17.txt", delim = "\t") %>% 
    rename(name_suffix = name_suffix_lbl,
           mname = middle_name) %>% 
    mutate_if(is.character, str_squish) %>% 
    mutate(id_b = row_number()))

(df_a_mod <- 
  df_a %>% 
  preprocess_data(df_dob))

(df_b_mod <- 
    df_b %>% 
    preprocess_data(df_dob))

# df_a_mod <- df_a_mod %>%
#   filter(!is.na(birth_year)) %>% 
#   prep_data() %>%
#     mess_data(df_error_table %>% 
#                 mutate(amount = amount*40/10)) %>% 
#     pluck("df_secondary") %>% 
#     select(-file, -id) %>% 
#     mutate_if(is.character, str_to_upper) %>% 
#     mutate(birth_year = as.integer(birth_year)) %>% 
#     select(-ffreq, -lfreq) %>% 
#     add_count(fname) %>%
#     rename(ffreq = n) %>% 
#     add_count(lname) %>% 
#     rename(lfreq = n) %>% 
#     mutate(ffreq = scale(ffreq),
#            lfreq = scale(lfreq))

```


## Match generation

1. Extract exact matches
2. Extract voter id matches
3. Filter out exact matches from voter id matches -> matches

```{r matches}
(df_exact_matches <- 
    df_a_mod %>% 
    select(id_a, fname, mname, lname, 
           dob, gender_code, race_code) %>% 
    inner_join(df_b_mod %>% 
                 select(id_b, fname, mname, lname, 
                        dob, gender_code, race_code)) %>% 
    select(starts_with("id")))

(df_vrn_matches <- 
  df_a_mod %>% 
  select(id_a, voter_reg_num) %>% 
  inner_join(df_b_mod %>% 
               select(id_b, voter_reg_num), 
             by = "voter_reg_num") %>% 
  select(starts_with("id")) %>% 
  mutate(match = "match") %>% 
  distinct())

  
(df_matches_unexact <- 
  df_vrn_matches  %>% 
  anti_join(df_exact_matches) %>% 
  left_join(df_a_mod, by = "id_a") %>% 
  left_join(df_b_mod, by = "id_b", suffix = c("_a", "_b")) %>% 
  mutate(pair_id = row_number()))

data_path <- "data/paper2/"
data_path_file <- function(file_name) glue("{data_path}{file_name}")

if(dir_exists(data_path)){
  dir_create(data_path)
}

(df_matches_unexact %>% 
  write_rds(data_path_file("df_matches_unexact.rds")))
```

## Unmatch generation

```{r unmatches, eval=FALSE}
df_match_block <- 
  df_matches_unexact %>% 
  select(matches(or("id", "fname", "lname", "dob"))) %>% 
  mutate(fname_soundex_a = soundex(fname_a),
         fname_soundex_b = soundex(fname_b),
         fname_dm_a = map(fname_a, DoubleMetaphone),
         fname_dm1_a = map_chr(fname_dm_a, 1),
         fname_dm2_a = map_chr(fname_dm_a, 2),
         fname_dm_b = map(fname_b, DoubleMetaphone),
         fname_dm1_b = map_chr(fname_dm_b, 1),
         fname_dm2_b = map_chr(fname_dm_b, 2),
         lname_soundex_a = soundex(lname_a),
         lname_soundex_b = soundex(lname_b),
         lname_dm_a = map(lname_a, DoubleMetaphone),
         lname_dm1_a = map_chr(lname_dm_a, 1),
         lname_dm2_a = map_chr(lname_dm_a, 2),
         lname_dm_b = map(lname_b, DoubleMetaphone),
         lname_dm1_b = map_chr(lname_dm_b, 1),
         lname_dm2_b = map_chr(lname_dm_b, 2)
         ) %>% 
  select(-fname_dm_a, -fname_dm_b) #, -lname_dm_a, -lname_dm_b)

df_a_block <- 
  df_a_mod %>% 
  select(id_a, fname, lname) %>% 
  rename(fname_a = fname,
         lname_a = lname) %>% 
  mutate(fname_soundex_a = soundex(fname_a),
         fname_dm_a = map(fname_a, DoubleMetaphone),
         fname_dm1_a = map_chr(fname_dm_a, 1),
         fname_dm2_a = map_chr(fname_dm_a, 2),
         lname_soundex_a = soundex(lname_a),
         lname_dm_a = map(lname_a, DoubleMetaphone),
         lname_dm1_a = map_chr(lname_dm_a, 1),
         lname_dm2_a = map_chr(lname_dm_a, 2)) %>% 
  select(-fname_dm_a, -lname_dm_a)
  

df_b_block <- 
  df_b_mod %>% 
  select(id_b, fname, lname) %>% 
  rename(fname_b = fname,
         lname_b = lname) %>% 
  mutate(fname_soundex_b = soundex(fname_b),
         fname_dm_b = map(fname_b, DoubleMetaphone),
         fname_dm1_b = map_chr(fname_dm_b, 1),
         fname_dm2_b = map_chr(fname_dm_b, 2),
         lname_soundex_b = soundex(lname_b),
         lname_dm_b = map(lname_b, DoubleMetaphone),
         lname_dm1_b = map_chr(lname_dm_b, 1),
         lname_dm2_b = map_chr(lname_dm_b, 2)) %>% 
  select(-fname_dm_b, -lname_dm_b)

df_match_block_a <- 
  df_match_block %>% 
  select(contains("_a")) 

df_match_block_b <- 
  df_match_block %>% 
  select(contains("_b")) 

df_all_combos <- 
  bind_rows(
      df_match_block_a %>% 
      inner_join(df_b_block, by = c("fname_soundex_a" = "fname_soundex_b")) %>% 
      select(id_a, id_b),
      
    df_match_block_a %>% 
      inner_join(df_b_block, by = c("fname_dm1_a" = "fname_dm1_b")) %>% 
      select(id_a, id_b),
    
    df_match_block_a %>% 
      inner_join(df_b_block, by = c("fname_dm2_a" = "fname_dm2_b")) %>% 
      select(id_a, id_b),
    
    df_match_block_a %>%
      inner_join(df_b_block, by = c("lname_soundex_a" = "lname_soundex_b")) %>%
      select(id_a, id_b),

    df_match_block_a %>%
      inner_join(df_b_block, by = c("lname_dm1_a" = "lname_dm1_b")) %>%
      select(id_a, id_b),

    df_match_block_a %>%
      inner_join(df_b_block, by = c("lname_dm2_a" = "lname_dm2_b")) %>%
      select(id_a, id_b),

    df_match_block_b %>% 
      inner_join(df_a_block, by = c("fname_soundex_b" = "fname_soundex_a")) %>% 
      select(id_a, id_b),
    
    df_match_block_b %>% 
      inner_join(df_a_block, by = c("fname_dm1_b" = "fname_dm1_a")) %>% 
      select(id_a, id_b),
    
    df_match_block_b %>% 
      inner_join(df_a_block, by = c("fname_dm2_b" = "fname_dm2_a")) %>% 
      select(id_a, id_b),
    
    df_match_block_b %>%
      inner_join(df_a_block, by = c("lname_soundex_b" = "lname_soundex_a")) %>%
      select(id_a, id_b),

    df_match_block_b %>%
      inner_join(df_a_block, by = c("lname_dm1_b" = "lname_dm1_a")) %>%
      select(id_a, id_b),

    df_match_block_b %>%
      inner_join(df_a_block, by = c("lname_dm2_b" = "lname_dm2_a")) %>%
      select(id_a, id_b)
  ) %>% 
  distinct() %>% 
  anti_join(df_vrn_matches) %>% 
  anti_join(df_exact_matches)

# added
df_all_combos <- 
  df_all_combos %>% 
  left_join(df_a_mod %>% select(id_a, dob), 
            by = "id_a") %>% 
  left_join(df_b_mod %>% select(id_b, dob), 
            by = "id_b", 
            suffix = c("_a", "_b")) %>%
  filter(abs(year(dob_a) - year(dob_b)) <=2|
         stringdist(year(dob_a),year(dob_b)) <= 1) %>% 
  select(-dob_a, -dob_b)

df_all_combos_nested <- 
  df_all_combos %>% 
  left_join(df_a_mod, by = "id_a") %>% 
  left_join(df_b_mod, by = "id_b", suffix = c("_a", "_b")) %>% 
  group_by(id_a, id_b) %>% 
  nest()

df_weight_vector <- 
  df_a_mod %>% 
  bind_rows(df_b_mod) %>% 
  select(fname, mname, lname, gender_code, race_code, dob) %>% 
  mutate(year = year(dob),
         md = glue("{month(dob)}-{day(dob)}")) %>% 
  # select(-dob) %>% 
  summarise_all(n_unique) %>% 
  rename_all(rename_weight) %>%
  gather(col, val) %>% 
  mutate(val = val/sum(val),
         val = map2_dbl(col, val, function(x,y){
           names(y) <- x
           y
         })) %>% 
  arrange(col)

weight_vector <- df_weight_vector$val
names(weight_vector) <- df_weight_vector$col

number_of_sims <- nrow(df_all_combos_nested)
message(glue("Number of rows: {number_of_sims}"))
time_start <- Sys.time()
df_all_combos_nested_sim <- 
  df_all_combos_nested %>% 
  mutate(x = map2_dbl(row_number(), data, function(i, df){
    if(i%%1000 == 0){
      message(
        glue("{i}/{number_of_sims} records: {round(i*100/number_of_sims, 2)}%- {round(as.numeric(Sys.time()-time_start,units='mins'), 1)} minutes elapsed"))
      # message(Sys.time() - time_start)
    }
    calculate_hamming_fields(df, weight_vector)
  }),
  match = "unmatch")

k <- 1
(df_unmatches_unexact <- 
  df_all_combos_nested_sim %>% 
  # semi_join(df_matches_unexact, by = "id_a") %>%
  group_by(id_a) %>% 
  arrange(desc(x), .by_group = T) %>% 
  slice(1:k) %>% 
  ungroup() %>% 
  bind_rows(
    df_all_combos_nested_sim %>% 
    # semi_join(df_matches_unexact, by = "id_b") %>%
    group_by(id_b) %>% 
    arrange(desc(x), .by_group = T) %>% 
    slice(1:k) %>% 
    ungroup() 
  ) %>%
  arrange(desc(x)) %>% 
  select(starts_with("id"), match) %>% 
  distinct() %>% 
  slice(1:(4*nrow(df_matches_unexact))) %>% 
  left_join(df_a_mod, by = "id_a") %>%
  left_join(df_b_mod, by = "id_b", suffix = c("_a", "_b")) %>%
  mutate(pair_id = 986398  + row_number())) 

df_unmatches_unexact %>% vectors_to_pairs() %>% View()
df_all_combos_nested_sim %>% 
  left_join(df_a_mod, by = "id_a") %>%
  left_join(df_b_mod, by = "id_b", suffix = c("_a", "_b")) %>%
  arrange(desc(x), id_a) %>% 
  vectors_to_pairs() %>% 
  View()

(df_unmatches_unexact %>% 
  write_rds(data_path_file("df_unmatches_unexact.rds")))
```

```{r read_executed_unmatch, echo=FALSE}
read_data("data/paper2/df_unmatches_unexact.rds")
df_unmatches_unexact
```

## Pair Generation

```{r pairs}
set.seed(1)
df_pairs <- 
  df_unmatches_unexact %>%
  bind_rows(df_matches_unexact) %>% 
  sample_n((nrow(.)))

(df_pairs %>% 
  write_rds(data_path_file("df_pairs.rds")))

(df_pairs %>% 
  vectors_to_pairs())
```


# Disturbing data

The above pipeline was wrapped into a function, so that database A can be made noisy and the pair generation can be repeated. 

```
df_error_table <- 
  read_csv("R/paper2/error_table.csv")

set.seed(13)
df_messed_collection <- 
  tibble(error_rate = seq(0, 40, 10)) %>% 
    mutate(df_a_mod = map(error_rate, function(e){
      # browser()
      df_a_mod %>%
        prep_data() %>%
        mess_data(df_error_table %>% 
                    mutate(amount = amount*e/10)) %>% 
        pluck("df_secondary") %>% 
        select(-file, -id) %>% 
        mutate_if(is.character, str_to_upper) %>% 
        mutate(birth_year = as.integer(birth_year)) %>% 
        select(-ffreq, -lfreq) %>% 
        add_count(fname) %>%
        rename(ffreq = n) %>% 
        add_count(lname) %>% 
        rename(lfreq = n) %>% 
        mutate(ffreq = scale(ffreq),
               lfreq = scale(lfreq))
    }))

df_messed_collection <- 
  df_messed_collection %>% 
  mutate(df_pairs = map2(df_a_mod, error_rate, function(df_a_mod, e) {
    message("________________________")
    message(glue("Error rate: {e}%"))
    
    generate_pairs(df_a_mod = df_a_mod, 
                   df_b_mod = df_b_mod, 
                   data_pref = 
                     e %>% 
                     str_pad(width = 2, side = "left", pad = "0") %>% 
                     str_c("err_", .))
  }))

df_messed_collection %>%
  write_rds("data/paper2/error_data/df_messed_collection.rds")

df_messed_collection
```

```{r read df_pairs_collection, echo=FALSE}
(df_messed_collection <- 
  read_rds("data/paper2/error_data/df_messed_collection.rds"))
```


# Feature Engineering

Using a function called add_feature_vector to generate features. 

```
df_messed_collection <-
  df_messed_collection %>% 
  mutate(df_feature = map(df_pairs, function(df_pair){
    df_pair %>%
      add_feature_vector() %>%
      select(starts_with("metric"), match) %>%
      mutate(match = match %>% factor(levels = c("unmatch", "match"))) %>%
      as.data.frame()
  }))
  

df_messed_collection %>%
  write_rds("data/paper2/error_data/df_feature_collection.rds")
  
df_messed_collection
```

```{r read df_feature_collection, echo=FALSE}
(df_messed_collection <- 
  read_rds("data/paper2/error_data/df_feature_collection.rds"))
```

One df_feature dataframe looks like these.
```{r view df_feature}
df_messed_collection$df_feature[[1]]
```


# Modeling

## Modeling setup

```{r train_test_split}
sample_strat <- function(df, n = 5000){
  match <- df$match
  row_num <- 1:nrow(df)
  
  m = ceiling(n/6)
  u = n - m
  
  indices_m = sample(row_num[match == "match"], m)
  indices_u = sample(row_num[match == "unmatch"], u)
  
  sample(c(indices_u, indices_m), n)
}

df_all <- 
  df_messed_collection$df_feature[[1]]

set.seed(23)
df_messed_collection <- 
  df_messed_collection %>% 
  mutate(train_indices = map(df_pairs, sample_strat, n = 5000),
         test_indices = map2(df_feature, train_indices, function(df, t){
           (1:nrow(df))[-t]
         }),
         df_train = map2(df_feature, train_indices, function(df, t){
           df[t, ]
         }),
         df_test =  
           pmap(list(df_pairs, df_feature, test_indices), 
                         function(pairs, df, v){
                           bind_cols(pairs, df) %>% 
                             as.data.frame() %>% 
                             .[v, ]
                         }))


train_control <- 
  trainControl(method = "cv", 
               number = 10,
               verboseIter = FALSE,
               savePredictions = TRUE,
               classProbs = TRUE)
```


```
  
df_messed_collection <- 
  df_messed_collection %>% 
  mutate(
    model_rf = map(df_train, function(df_tr){
      # browser()
      set.seed(3)
      train(match ~ .,
            df_tr,
            trControl = train_control,
            tuneGrid = expand.grid(.mtry = seq(1, 6, 1)),
            importance = TRUE,
            keep.forest= TRUE,
            ntree = 350,
            method = "rf")
    }),
    model_svm_radial = map(df_train, function(df_tr){
        # browser()
        set.seed(3)
        train(match ~ .,
              df_tr,
              trControl = train_control,
              method = "svmRadial")
      }),
    model_svm_linear = map(df_train, function(df_tr){
      # browser()
      set.seed(3)
      train(match ~ .,
            df_tr,
            trControl = train_control,
            method = "svmLinear") 
  })
  )



df_messed_collection %>% 
  write_rds("data/paper2/error_data/df_messed_collection_models.rds")
  
df_messed_collection
```

```{r read_models,echo=FALSE}
(df_messed_collection <- 
  read_rds("data/paper2/error_data/df_messed_collection_models.rds"))

df_messed_collection <- 
  df_messed_collection %>% 
  gather(model, model_obj, starts_with("model")) %>% 
  select(model, everything()) %>% 
  mutate(model = model %>% str_replace("model_", ""))
```


```{r test_set_evaluation}
df_messed_collection <- 
  df_messed_collection %>%
  mutate(
    results = map2(model_obj, df_test, function(model, df){
      df %>%
      mutate(pair_id = 1:nrow(.)) %>%
      evaluate_model(model, df_test = ., plot_roc = F)
    }),
    metrics = map(results, ~.x$metrics$df_metric_table),
    confusion_matrix = map(results, ~.x$metrics$confusion_matrix),
    roc_curve = map(results, ~.x$metrics$roc_curve),
    pred_confidence = map(results, ~.x$confidence)
  )

df_model_metrics <-
  df_messed_collection %>%
  select(model, error_rate, metrics) %>%
  unnest(metrics)



plot_roc_all(df_messed_collection %>% filter(model == "svm_radial"),
             model_col = error_rate)

df_model_metrics %>%
  filter(metric %in% c("accuracy", "precision", "recall", "f1","auc")) %>%
  ggplot(aes(error_rate, value, group = metric, col = metric)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(breaks = seq(0, 1, 0.2), 
                     limits = c(0, 1), 
                     minor_breaks = NULL)+
  theme_light()

df_model_metrics %>% 
  filter(metric %in% c("accuracy", "precision", "recall", "f1","auc")) %>%
  ggplot(aes(model, value, fill = model)) +
  geom_col(position = "dodge") +
  facet_grid(error_rate~metric) +
  coord_flip()
  

```