---
title: "Paper flow"
author: "Gurudev Ilangovan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: tibble
    highlight: tango
    theme: flatly
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: false
      smooth_scroll: true
    number_sections: true 
    code_folding: hide
---

```{r setup, results="hide"}
knitr::opts_chunk$set(cache = F, message = FALSE)
source("R/paper2/utils.R")
theme_set(theme_light())
```

# Data Generation - The pipeline

## Preprocessing

1. Read April 2013 data and March 17 data. 
2. Do some basic preprocessing
  - Assign ids
  - Calculate age from birth year
  - Add scaled frequencies
```{r preprocess}

df_dob <- 
  read_csv("data/paper2/raw/dob.csv", 
             col_types = cols(voter_registration_number = "c")) %>% 
  select(voter_reg_num = voter_registration_number, dob = bday) %>% 
  mutate(dob_twin = dob)

(df_a <- 
    read_delim("data/paper2/raw/apr13.txt", delim = "\t") %>% 
    rename(name_suffix = name_sufx_cd,
           mname = midl_name) %>% 
    mutate_if(is.character, str_squish))

  
(df_b <- 
    read_delim("data/paper2/raw/mar17.txt", delim = "\t") %>% 
    rename(name_suffix = name_suffix_lbl,
           mname = middle_name) %>% 
    mutate_if(is.character, str_squish))

(df_a_mod <- 
  df_a %>% 
  preprocess_data(df_dob) %>% 
  filter(!is.na(dob)) %>% 
  prep_data() %>% 
  mess_data(read_csv("R/paper2/error_table.csv") %>% 
              mutate(amount = amount*4)) %>% 
  pluck("df_secondary") %>% 
  select(-file,-id))

(df_b_mod <- 
    df_b %>% 
    preprocess_data(df_dob) %>% 
    filter(!is.na(dob)))

df_a_mod <- 
  df_a_mod %>% 
    mutate(id_a = row_number())

df_b_mod <- 
  df_b_mod %>% 
    mutate(id_b = row_number())

# df_a_mod <- df_a_mod %>%
#   filter(!is.na(birth_year)) %>% 
#   prep_data() %>%
#     mess_data(df_error_table %>% 
#                 mutate(amount = amount*40/10)) %>% 
#     pluck("df_secondary") %>% 
#     select(-file, -id) %>% 
#     mutate_if(is.character, str_to_upper) %>% 
#     mutate(birth_year = as.integer(birth_year)) %>% 
#     select(-ffreq, -lfreq) %>% 
#     add_count(fname) %>%
#     rename(ffreq = n) %>% 
#     add_count(lname) %>% 
#     rename(lfreq = n) %>% 
#     mutate(ffreq = scale(ffreq),
#            lfreq = scale(lfreq))

```


## Match generation

1. Extract exact matches
2. Extract voter id matches
3. Filter out exact matches from voter id matches -> matches

```{r matches}
(df_exact_matches <- 
    df_a_mod %>% 
    select(id_a, fname, lname, 
           dob, gender_code, race_code) %>% 
    inner_join(df_b_mod %>% 
                 select(id_b, fname, lname, 
                        dob, gender_code, race_code)) %>% 
    select(starts_with("id")))

(df_vrn_matches <- 
  df_a_mod %>% 
  select(id_a, voter_reg_num) %>% 
  inner_join(df_b_mod %>% 
               select(id_b, voter_reg_num), 
             by = "voter_reg_num") %>% 
  select(starts_with("id")) %>% 
  mutate(match = "match") %>% 
  distinct())

  
(df_matches_unexact <- 
  df_vrn_matches  %>% 
  anti_join(df_exact_matches) %>% 
  left_join(df_a_mod, by = "id_a") %>% 
  left_join(df_b_mod, by = "id_b", suffix = c("_a", "_b")) %>% 
  mutate(pair_id = row_number()))

data_path <- "data/paper2/"
data_path_file <- function(file_name) glue("{data_path}{file_name}")

if(dir_exists(data_path)){
  dir_create(data_path)
}

(df_matches_unexact %>% 
  write_rds(data_path_file("df_matches_unexact.rds")))
```

## Unmatch generation

```{r unmatches, eval=FALSE}
df_blocks <- 
  bind_rows(
    
    df_matches_unexact %>% 
      select(id_a, fname_a) %>%
      inner_join(df_b_mod %>% select(id_b, fname),
                 by = c("fname_a" = "fname")) %>% 
      select(id_a, id_b),
    
    df_matches_unexact %>% 
      select(id_b, fname_b) %>%
      inner_join(df_a_mod %>% select(id_a, fname),
                 by = c("fname_b" = "fname")) %>% 
      select(id_a, id_b),
    
    df_matches_unexact %>% 
      select(id_a, lname_a) %>%
      inner_join(df_b_mod %>% select(id_b, lname),
                 by = c("lname_a" = "lname")) %>% 
      select(id_a, id_b),
    
    df_matches_unexact %>% 
      select(id_b, lname_b) %>%
      inner_join(df_a_mod %>% select(id_a, lname),
                 by = c("lname_b" = "lname")) %>% 
      select(id_a, id_b),
    
    df_matches_unexact %>% 
      select(id_a, dob_a) %>%
      inner_join(df_b_mod %>% select(id_b, dob),
                 by = c("dob_a" = "dob")) %>% 
      select(id_a, id_b),
    
    df_matches_unexact %>% 
      select(id_b, dob_b) %>%
      inner_join(df_a_mod %>% select(id_a, dob),
                 by = c("dob_b" = "dob")) %>% 
      select(id_a, id_b)
    
  ) %>% 
  distinct() %>% 
  anti_join(df_exact_matches, by = c("id_a", "id_b")) %>% 
  anti_join(df_vrn_matches, by = c("id_a", "id_b")) %>% 
  attach_dbs_to_ids() %>% 
  distinct()

df_blocks <- 
  df_blocks %>% 
  mutate(fname_jw = stringdist(fname_a, fname_b, "jw", p = 0.1), 
         lname_jw = stringdist(lname_a, lname_b, "lv", p = 0.1), 
         day_match = day(dob_a) == day(dob_b),
         month_match = month(dob_a) == month(dob_b),
         year_match = year(dob_a) == year(dob_b),
         swap_match = (day(dob_a) == month(dob_b)) & (day(dob_b) == month(dob_a))) %>% 
  select(id_a, id_b, contains("jw"), contains("match"))



df_thresholds <- 
  df_blocks %>% 
  mutate(thresh_fname = fname_jw < 0.15,
         thresh_lname = lname_jw < 0.15,
         thresh_dob = 
           (day_match + month_match + swap_match + year_match) >= 2,
         thresh_criteria = thresh_fname + thresh_lname + thresh_dob,
         
         thresh_weight = 
           (1 - fname_jw) + 
           (1 - lname_jw) + 
           (day_match + month_match + swap_match + year_match)/3) %>% 
  select(contains("id"), contains("thresh"))

df_thresholds %>% 
  ggplot(aes(thresh_weight)) +
  geom_histogram()

df_thresholds %>% 
  count(thresh_criteria)

(df_unmatches <- 
  df_thresholds %>% 
  sample_n(nrow(.)) %>% 
  arrange(desc(thresh_criteria)) %>% 
  # top_n(4*nrow(df_matches_unexact), thresh_weight) %>% 
  slice(1:(4*nrow(df_matches_unexact))) %>% 
  select(contains(("id"))) %>% 
  mutate(match = "unmatch") %>% 
  attach_dbs_to_ids())

df_unmatches %>% 
  vectors_to_pairs() %>% 
  View()


```

```{r read_executed_unmatch, echo=FALSE}
read_data("data/paper2/df_unmatches_unexact.rds")
df_unmatches_unexact
```

## Pair Generation

```{r pairs}
set.seed(1)
df_pairs <- 
  df_unmatches_unexact %>%
  bind_rows(df_matches_unexact) %>% 
  sample_n((nrow(.)))

(df_pairs %>% 
  write_rds(data_path_file("df_pairs.rds")))

(df_pairs %>% 
  vectors_to_pairs())
```


# Disturbing data

The above pipeline was wrapped into a function, so that database A can be made noisy and the pair generation can be repeated. 

```
df_error_table <- 
  read_csv("R/paper2/error_table.csv")

set.seed(13)
df_messed_collection <- 
  tibble(error_rate = seq(0, 40, 10)) %>% 
    mutate(df_a_mod = map(error_rate, function(e){
      # browser()
      df_a_mod %>%
        prep_data() %>%
        mess_data(df_error_table %>% 
                    mutate(amount = amount*e/10)) %>% 
        pluck("df_secondary") %>% 
        select(-file, -id) %>% 
        mutate_if(is.character, str_to_upper) %>% 
        mutate(birth_year = as.integer(birth_year)) %>% 
        select(-ffreq, -lfreq) %>% 
        add_count(fname) %>%
        rename(ffreq = n) %>% 
        add_count(lname) %>% 
        rename(lfreq = n) %>% 
        mutate(ffreq = scale(ffreq),
               lfreq = scale(lfreq))
    }))

df_messed_collection <- 
  df_messed_collection %>% 
  mutate(df_pairs = map2(df_a_mod, error_rate, function(df_a_mod, e) {
    message("________________________")
    message(glue("Error rate: {e}%"))
    
    generate_pairs(df_a_mod = df_a_mod, 
                   df_b_mod = df_b_mod, 
                   data_pref = 
                     e %>% 
                     str_pad(width = 2, side = "left", pad = "0") %>% 
                     str_c("err_", .))
  }))

df_messed_collection %>%
  write_rds("data/paper2/error_data/df_messed_collection.rds")

df_messed_collection
```

```{r read df_pairs_collection, echo=FALSE}
(df_messed_collection <- 
  read_rds("data/paper2/error_data/df_messed_collection.rds"))
```


# Feature Engineering

Using a function called add_feature_vector to generate features. 

```
df_messed_collection <-
  df_messed_collection %>% 
  mutate(df_feature = map(df_pairs, function(df_pair){
    df_pair %>%
      add_feature_vector() %>%
      select(starts_with("metric"), match) %>%
      mutate(match = match %>% factor(levels = c("unmatch", "match"))) %>%
      as.data.frame()
  }))
  

df_messed_collection %>%
  write_rds("data/paper2/error_data/df_feature_collection.rds")
  
df_messed_collection
```

```{r read df_feature_collection, echo=FALSE}
(df_messed_collection <- 
  read_rds("data/paper2/error_data/df_feature_collection.rds"))
```

One df_feature dataframe looks like these.
```{r view df_feature}
df_messed_collection$df_feature[[1]]
```


# Modeling

## Modeling setup

```{r train_test_split}
sample_strat <- function(df, n = 5000){
  match <- df$match
  row_num <- 1:nrow(df)
  
  m = ceiling(n/6)
  u = n - m
  
  indices_m = sample(row_num[match == "match"], m)
  indices_u = sample(row_num[match == "unmatch"], u)
  
  sample(c(indices_u, indices_m), n)
}

df_all <- 
  df_messed_collection$df_feature[[1]]

set.seed(23)
df_messed_collection <- 
  df_messed_collection %>% 
  mutate(train_indices = map(df_pairs, sample_strat, n = 5000),
         test_indices = map2(df_feature, train_indices, function(df, t){
           (1:nrow(df))[-t]
         }),
         df_train = map2(df_feature, train_indices, function(df, t){
           df[t, ]
         }),
         df_test =  
           pmap(list(df_pairs, df_feature, test_indices), 
                         function(pairs, df, v){
                           bind_cols(pairs, df) %>% 
                             as.data.frame() %>% 
                             .[v, ]
                         }))


train_control <- 
  trainControl(method = "cv", 
               number = 10,
               verboseIter = FALSE,
               savePredictions = TRUE,
               classProbs = TRUE)
```


```
  
df_messed_collection <- 
  df_messed_collection %>% 
  mutate(
    model_rf = map(df_train, function(df_tr){
      # browser()
      set.seed(3)
      train(match ~ .,
            df_tr,
            trControl = train_control,
            tuneGrid = expand.grid(.mtry = seq(1, 6, 1)),
            importance = TRUE,
            keep.forest= TRUE,
            ntree = 350,
            method = "rf")
    }),
    model_svm_radial = map(df_train, function(df_tr){
        # browser()
        set.seed(3)
        train(match ~ .,
              df_tr,
              trControl = train_control,
              method = "svmRadial")
      }),
    model_svm_linear = map(df_train, function(df_tr){
      # browser()
      set.seed(3)
      train(match ~ .,
            df_tr,
            trControl = train_control,
            method = "svmLinear") 
  })
  )



df_messed_collection %>% 
  write_rds("data/paper2/error_data/df_messed_collection_models.rds")
  
df_messed_collection
```

```{r read_models,echo=FALSE}
(df_messed_collection <- 
  read_rds("data/paper2/error_data/df_messed_collection_models.rds"))

df_messed_collection <- 
  df_messed_collection %>% 
  gather(model, model_obj, starts_with("model")) %>% 
  select(model, everything()) %>% 
  mutate(model = model %>% str_replace("model_", ""))
```


```{r test_set_evaluation}
df_messed_collection <- 
  df_messed_collection %>%
  mutate(
    results = map2(model_obj, df_test, function(model, df){
      df %>%
      mutate(pair_id = 1:nrow(.)) %>%
      evaluate_model(model, df_test = ., plot_roc = F)
    }),
    metrics = map(results, ~.x$metrics$df_metric_table),
    confusion_matrix = map(results, ~.x$metrics$confusion_matrix),
    roc_curve = map(results, ~.x$metrics$roc_curve),
    pred_confidence = map(results, ~.x$confidence)
  )

df_model_metrics <-
  df_messed_collection %>%
  select(model, error_rate, metrics) %>%
  unnest(metrics)



plot_roc_all(df_messed_collection %>% filter(model == "svm_radial"),
             model_col = error_rate)

df_model_metrics %>%
  filter(metric %in% c("accuracy", "precision", "recall", "f1","auc")) %>%
  ggplot(aes(error_rate, value, group = metric, col = metric)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(breaks = seq(0, 1, 0.2), 
                     limits = c(0, 1), 
                     minor_breaks = NULL)+
  theme_light()

df_model_metrics %>% 
  filter(metric %in% c("accuracy", "precision", "recall", "f1","auc")) %>%
  ggplot(aes(model, value, fill = model)) +
  geom_col(position = "dodge") +
  facet_grid(error_rate~metric) +
  coord_flip()
  

```